Random Forests", OAs

### 2024-01-13 src/oa_RF.Rmd
refined model OA

# Build OA for GB
oa.gb <- rbind(oa.ew, oa.sc, oa.ni)
rm(oa.ew, oa.sc, oa.ni)

@@

```{r}
#oa.sf <- st_as_sf(oa.gb)

oa.full <- replicate(17, oa.gb %>% as_tibble(), simplify = FALSE) %>%
  bind_rows(.id = 'id_') %>% 
  rename(year = id_) %>% 
  mutate(year = as.numeric(year) + 1995) %>% 
  dplyr::select(id, year)

@@

```{r}
# oa centroids
# oa.gb.c <- (rgeos::gCentroid(oa.gb, byid=TRUE))@coords %>% as.data.frame()
# oa.gb.c$id <- row.names(oa.gb.c)  #as_tibble(rownames = NA) %>% 
#   mutate(id = row.names())

# oa.gb.c <- gCentroid(oa.gb, byid=TRUE)@coords %>% 
#   as.data.frame() %>% 
#   add_rownames(var = "id")
sf_use_s2(FALSE)
oa.gb.c <- st_centroid(oa.gb) %>%
  st_coordinates() %>%
  as.data.frame() %>%
  #add_rownames(var = "id") %>% 
  bind_cols(oa.gb %>% dplyr::select(id))

# cities
city.names <- c("London, UK", 
"Birmingham, UK",
"Glasgow, UK",
"Liverpool, UK",
"Bristol, UK",
"Manchester, UK",
"Sheffield, UK",
"Leeds, UK",
"Edinburgh, UK",
"Leicester, UK")

@@

# cities
city.names <- c(
  "London", 
  "Birmingham",
  "Glasgow",
  "Liverpool",
  "Bristol",
  "Manchester",
  "Sheffield",
  "Leeds",
  "Edinburgh",
  "Leicester"
  )

@@

# Source: https://geoportal.statistics.gov.uk/
path.in <- paste0(path, "/data/raw/Local_Authority_Districts_(December_2021)_UK_BUC.geojson")
city.boundaries.sc <- st_read(path.geo) %>% 
  st_transform(4326) %>% 
  filter(grepl('Edinburgh|Glasgow', LAD21NM)) %>% 
  dplyr::select(OBJECTID, LAD21CD, LAD21NM) %>% 
  rename(code = LAD21CD,
         name = LAD21NM)

# merge
city.boundaries <- rbind(city.boundaries.ew, city.boundaries.sc)

@@

# retail.major.cetres <- retail.major.cetres.help %>% 
#   st_as_sf(coords = c("x", "y"), crs = 27700) %>%
#   st_transform(4326) %>%
#   st_coordinates() %>%
#   as_tibble() %>% 
#   bind_cols(retail.major.cetres.help$id) %>% 
#   rename(id = '...3') %>% 
#   left_join(retail@data %>% mutate(id = rownames(retail@data)), by = 'id')
retail.major.cetres <- retail.major.cetres.help %>% 
  # as_tibble() %>% 
  # bind_cols(retail.major.cetres.help$id) %>% 
  # #rename(id = '...3') %>% 
  left_join(retail %>% rownames_to_column(var = "id"), by = 'id')

@@

```{r}
dist <- distm(cbind(oa.gb.c$X, oa.gb.c$Y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist <- round((dist/1000),2) %>% 
  as_tibble()

names(dist) <- cities$address #city.names

dist <- dist %>% bind_cols(oa.gb.c$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

@@

# min distance
dist <- transform(dist, dist = do.call(pmin, dist[-1]))

# City name for minimum distance 
dist <- dist %>% mutate(dist.city.name = names(.)[max.col(.[2:11]*-1)+1L])

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% dplyr::select(oa11cd)) %>%
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>%
#   filter(country != "L" & country != "M" & country != "N") %>%
#   filter(!is.na(country)) %>%
#   complete(year, oa11cd, fill = list(n = 0)) %>%
#   filter(year!=1000,
#          !is.na(oa11cd)) %>%
#   dplyr::select(-country)

# tests
# test$country <- substring(test$oa11cd, 1, 1)
# unique(test$country)
# length(unique(test$oa11cd))

# calculate area
#oa.gb$area <- st_area(oa.gb) #/ 1000000

# Join with distance and area
df <- df %>% left_join(dist, by = c("id" = "oa11cd")) %>% 
  rename(oa11cd=id)  
  # left_join(oa.gb, by = c("oa11cd" = "id")) %>% 
  # relocate(area, .after = n) %>% 
  # mutate(area = area / 1000000,
  #        density = n / area) %>% 
  # relocate(density, .after = area) %>% 
  # dplyr::select(-geometry)

@@

```{r}
dist.retail <- distm(cbind(oa.gb.c$X, oa.gb.c$Y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail<- round((dist.retail/1000),2) %>% 
  as_tibble()

#retail.names <- retail.major.cetres$RC_ID
names(dist.retail) <- retail.major.cetres$RC_ID #city.names

dist.retail <- dist.retail %>% bind_cols(oa.gb.c$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

# This efficiently returns the name of the column with the shortest distance
dist.retail <- dist.retail %>% mutate(dist.retail.name = names(.)[max.col(.[2:6424]*-1)+1L])

@@

# Minimum distance 
dist.retail <- transform(dist.retail, dist.retail = do.call(pmin, dist.retail[2:6424]))

dist.retail <- dist.retail  %>% dplyr::select(oa11cd, dist.retail.name, dist.retail)
# 232,296 
#sapply(dist.retail, function(x) sum(is.na(x))) #0

### TO DELETE

# # spatial join retail centroids into OA
# retail.major.cetres.help <- st_centroid(retail) %>% 
#   st_transform(4326)
# 
# # lookup obj with retail id and OA id
# help <- st_join(retail.major.cetres.help, oa.gb) %>% 
#   as_tibble %>% 
#   mutate(dist.retail.name = row_number(),
#          dist.retail.name = paste0("V", dist.retail.name)) %>% 
#   dplyr::select(id, dist.retail.name) %>% 
#   rename(oa11cd.retail = id)
# 
# dist.retail <- dist.retail %>% 
#   left_join(help, by = c('dist.retail.name' = 'dist.retail.name')) %>% 
#   dplyr::select(-dist.retail.name)
# sapply(dist.retail, function(x) sum(is.na(x))) 
# # 1 retail centre is missing, because the centroid falls in the water
# 
# dist.retail %>% filter(is.na(oa11cd.retail))
# missing.retail.centre <- retail.major.cetres.help %>% filter(RC_ID=="RC_EW_24")
# st_nearest_feature(missing.retail.centre, oa.gb)
# oa.gb[91986,] # missing OA: E00094765.
# 
# dist.retail <- dist.retail %>%
#   mutate(oa11cd.retail = ifelse(is.na(oa11cd.retail), "E00094765", oa11cd.retail))
# 
# # dist.retail %>% distinct(dist.retail.name) #6405
# # help %>% distinct(dist.retail.name) # 6423 
# # dist.retail %>% distinct(oa11cd.retail) #6217 as there are multiple centres in an OA

@@

sf_use_s2(FALSE)
city.boundaries.oa <- st_join(oa.gb, city.boundaries, join = st_intersects) %>% 
  as_tibble() %>% 
  filter(!is.na(name)) %>% 
  dplyr::select(id, name) %>% 
  mutate(name = ifelse(name == "City of Edinburgh", "Edinburgh", name)) %>% 
  mutate(name = ifelse(name == "Glasgow City", "Glasgow", name))

@@

df <- df %>% left_join(london.boundaries.help, by = c("year" = "year"))
#sapply(df, function(x) sum(is.na(x)))
```

@@

retail.oa <- st_join(oa.gb, retail, join = st_intersects) %>% 
  as_tibble() %>% 
  filter(!is.na(RC_ID)) %>% 
  dplyr::select(id, RC_ID)

# st_join(oa.gb, retail, join = st_is_within_distance, dist = 500) %>% 
#   as_tibble() %>% 
#   filter(!is.na(RC_ID)) %>% 
#   dplyr::select(id, RC_ID)
# 
# st_filter(oa.gb, retail,  .pred = st_is_within_distance, dist = 100) %>% 
#   as_tibble() %>% 
#   filter(!is.na(RC_ID)) %>% 
#   dplyr::select(id, RC_ID)

# h <- oa.gb %>% st_intersects(retail)

@@

retail.help <- df %>% inner_join(retail.oa, by = c("oa11cd" = "id")) %>% 
  group_by(RC_ID, year) %>% 
  summarise(n.nearest.retail = sum(n)) %>% 
  mutate(n.nearest.retail.lag = dplyr::lag(n.nearest.retail)) %>% 
  ungroup()

@@

df <- df %>% left_join(retail.help, by = c("dist.retail.name" = "RC_ID", "year" = "year"))
#sapply(df_, function(x) sum(is.na(x)))
```

@@

```{r}
# Lookup: OA to regions
# **FIXED< DELETE IN TEST** NEED TO ADD NI. NOT A PROBLEM FOR NOW AS IT IS FIXED IN THE TEST SECTION
path.lookup <- paste0(path, "/data/raw/Output_Area_to_Region_(December_2011)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% dplyr::select(OA11CD, RGN11CD, RGN11NM)

# For growth:
df <- df %>% group_by(oa11cd) %>% 
  mutate(n.lag = dplyr::lag(n),
         growth = log(n/n.lag),
                    abs.growth = n - n.lag) %>% 
  relocate(n.lag, .after = n)

@@

```{r}
# sf_use_s2(FALSE)
# oa.c <- st_centroid(oa.gb)
# kn <- knearneigh(oa.c, k = 5)
# knn <- knn2nb(kn, row.names = NULL, sym = FALSE)
# knn.l <- nb2listw(knn)

path.out <- paste0(path, "/data/temp/oa_rf/all_OAs/knnl.RData")
# save(knn.l, file = path.out)
load(path.out)

@@

```{r}
# out.path <- paste0(path, "/data/temp/df_for_oa_rf.csv")
# df <- read_csv(out.path)
# df %>% write_csv(file = out.path)

@@

# There are no lags for 1996, so it is removed
df <- df %>% filter(year > 1996) %>% 
  dplyr::select(oa11cd, year, RGN11CD, n, abs.growth, n.l.slag, n.nearest.city.lag, 
                n.nearest.retail.lag, n.London.lag, London, dist, dist.retail) %>% #growth, abs.growth, RGN11NM, 
  mutate(London.v = n.London.lag / London,
         city.v = n.nearest.city.lag / dist,
         retail.v = n.nearest.retail.lag / (dist.retail + .1)) %>% 
  dplyr::select(-n.London.lag, -London, -n.nearest.city.lag, -dist, -n.nearest.retail.lag, -dist.retail)

@@

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken #1.3h

@@

#folds
k <- 10 # 7.09h for k=3

@@

detectCores()
cl <- makePSOCKcluster(8)
registerDoParallel(cl)

@@

regions <- df %>% distinct(RGN11CD)
regions <- as.vector(regions$RGN11CD)

@@

@@

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD==i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  #assign(paste0("model.all",as.character(i)), model.all)

  file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_", as.character(i), ".RData")
  save(model.all, file = file)
  rm(model.all)
}

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```

@@

```{r}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/data/temp/oa_rf/regions"), pattern = "*.RData", full.names = T)

for (i in filenames){
  load(file = i)
  i <- gsub("/home/nw19521/projects/web.diffusion/data/temp/oa_rf/regions/|.RData", "", i)
  assign(i, model.all)  
}

@@

```{r}
# train on one region, test on all the rest

>>>>

# Build OA for UK
oa.uk <- rbind(oa.ew, oa.sc, oa.ni)
rm(oa.ew, oa.sc, oa.ni)

@@

```{r}
#oa.sf <- st_as_sf(oa.uk)

oa.full <- replicate(17, oa.uk %>% as_tibble(), simplify = FALSE) %>%
  bind_rows(.id = 'id_') %>% 
  rename(year = id_) %>% 
  mutate(year = as.numeric(year) + 1995) %>% 
  dplyr::select(id, year)

@@

```{r}
# oa centroids
# oa.uk.c <- (rgeos::gCentroid(oa.uk, byid=TRUE))@coords %>% as.data.frame()
# oa.uk.c$id <- row.names(oa.uk.c)  #as_tibble(rownames = NA) %>% 
#   mutate(id = row.names())

# oa.uk.c <- gCentroid(oa.uk, byid=TRUE)@coords %>% 
#   as.data.frame() %>% 
#   add_rownames(var = "id")
sf_use_s2(FALSE)
oa.uk.c <- st_centroid(oa.uk) %>%
  st_coordinates() %>%
  as.data.frame() %>%
  #add_rownames(var = "id") %>% 
  bind_cols(oa.uk %>% dplyr::select(id))

# cities
city.names <- c("London, UK", 
"Birmingham, UK",
"Glasgow, UK",
"Liverpool, UK",
"Bristol, UK",
"Manchester, UK",
"Sheffield, UK",
"Leeds, UK",
"Edinburgh, UK",
"Leicester, UK",
"Belfast, UK")

@@

# # cities
# city.names <- c(
#   "London", 
#   "Birmingham",
#   "Glasgow",
#   "Liverpool",
#   "Bristol",
#   "Manchester",
#   "Sheffield",
#   "Leeds",
#   "Edinburgh",
#   "Leicester",
#   )

@@

# Source: https://geoportal.statistics.gov.uk/
path.in <- paste0(path, "/data/raw/Local_Authority_Districts_(December_2021)_UK_BUC.geojson")
city.boundaries.sc.ni <- st_read(path.in) %>% 
  st_transform(4326) %>% 
  filter(grepl('Edinburgh|Glasgow|Belfast', LAD21NM)) %>% 
  dplyr::select(OBJECTID, LAD21CD, LAD21NM) %>% 
  rename(code = LAD21CD,
         name = LAD21NM)

# merge
city.boundaries <- rbind(city.boundaries.ew, city.boundaries.sc.ni)
```

@@

# retail.major.cetres <- retail.major.cetres.help %>% 
#   st_as_sf(coords = c("x", "y"), crs = 27700) %>%
#   st_transform(4326) %>%
#   st_coordinates() %>%
#   as_tibble() %>% 
#   bind_cols(retail.major.cetres.help$id) %>% 
#   rename(id = '...3') %>% 
#   left_join(retail@data %>% mutate(id = rownames(retail@data)), by = 'id')
retail.major.cetres <- retail.major.cetres.help %>% 
  # as_tibble() %>% 
  # bind_cols(retail.major.cetres.help$id) %>% 
  # #rename(id = '...3') %>% 
  left_join(retail %>% rownames_to_column(var = "id"), by = 'id')
```

@@

```{r}
# NI
oa.uk.c.ni <- oa.uk.c %>% filter(str_detect(id, "^N"))

dist.ni <- distm(cbind(oa.uk.c.ni$X, oa.uk.c.ni$Y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist.ni <- round((dist.ni/1000),2) %>% 
  as_tibble()

names(dist.ni) <- cities$address #city.names

dist.ni <- dist.ni %>% bind_cols(oa.uk.c.ni$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

@@

# min distance
dist.ni <- transform(dist.ni, dist = do.call(pmin, dist.ni[-1]))

# City name for minimum distance 
dist.ni <- dist.ni %>% mutate(dist.city.name = names(.)[max.col(.[2:12]*-1)+1L])

# GB
oa.uk.c.gb <- oa.uk.c %>% filter(!str_detect(id, "^N"))

dist.gb <- distm(cbind(oa.uk.c.gb$X, oa.uk.c.gb$Y), cbind(cities$long, cities$lat), fun=distHaversine) 
dist.gb <- round((dist.gb/1000),2) %>% 
  as_tibble()

names(dist.gb) <- cities$address #city.names

dist.gb <- dist.gb %>% bind_cols(oa.uk.c.gb$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

# min distance
dist.gb <- transform(dist.gb, dist = do.call(pmin, dist.gb[-1]))

# City name for minimum distance 
dist.gb <- dist.gb %>% mutate(dist.city.name = names(.)[max.col(.[2:12]*-1)+1L])

# UK
dist <- rbind(dist.ni, dist.gb)

# calculate area
#oa.uk$area <- st_area(oa.uk) #/ 1000000

# Join with distance and area
df <- df %>% left_join(dist, by = c("id" = "oa11cd")) %>% 
  rename(oa11cd=id)

@@

```{r}
# dist.retail <- distm(cbind(oa.uk.c$X, oa.uk.c$Y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
# dist.retail <- round((dist.retail/1000),2) %>% 
#   as_tibble()

# NI
oa.uk.c.ni <- oa.uk.c %>% filter(str_detect(id, "^N"))
dist.retail.ni <- distm(cbind(oa.uk.c.ni$X, oa.uk.c.ni$Y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail.ni <- round((dist.retail.ni/1000),2) %>% 
  as_tibble()

names(dist.retail.ni) <- retail.major.cetres$RC_ID

dist.retail.ni <- dist.retail.ni %>% bind_cols(oa.uk.c.ni$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

# This efficiently returns the name of the column with the shortest distance
dist.retail.ni <- dist.retail.ni %>% mutate(dist.retail.name = names(.)[max.col(.[2:6424]*-1)+1L])

@@

# Minimum distance 
dist.retail.ni <- transform(dist.retail.ni, dist.retail = do.call(pmin, dist.retail.ni[2:6424])) 
dist.retail.ni <- dist.retail.ni  %>% dplyr::select(oa11cd, dist.retail.name, dist.retail)

# GB
oa.uk.c.gb <- oa.uk.c %>% filter(!str_detect(id, "^N"))
dist.retail.gb <- distm(cbind(oa.uk.c.gb$X, oa.uk.c.gb$Y), cbind(retail.major.cetres$X, retail.major.cetres$Y), fun=distHaversine) 
dist.retail.gb <- round((dist.retail.gb/1000),2) %>% 
  as_tibble()

names(dist.retail.gb) <- retail.major.cetres$RC_ID

dist.retail.gb <- dist.retail.gb %>% bind_cols(oa.uk.c.gb$id) %>% 
  rename(oa11cd = last_col()) %>% 
  relocate(oa11cd)

# This efficiently returns the name of the column with the shortest distance
dist.retail.gb <- dist.retail.gb %>% mutate(dist.retail.name = names(.)[max.col(.[2:6424]*-1)+1L])

# Minimum distance 
dist.retail.gb <- transform(dist.retail.gb, dist.retail = do.call(pmin, dist.retail.gb[2:6424])) 
dist.retail.gb <- dist.retail.gb  %>% dplyr::select(oa11cd, dist.retail.name, dist.retail)

# UK
dist.retail <- rbind(dist.retail.ni, dist.retail.gb)

@@

sf_use_s2(FALSE)
city.boundaries.oa <- st_join(oa.uk, city.boundaries, join = st_intersects) %>% 
  as_tibble() %>% 
  filter(!is.na(name)) %>% 
  dplyr::select(id, name) %>% 
  mutate(name = ifelse(name == "City of Edinburgh", "Edinburgh", name)) %>% 
  mutate(name = ifelse(name == "Glasgow City", "Glasgow", name))

@@

df <- df %>% left_join(london.boundaries.help, by = c("year" = "year"))

@@

retail.oa <- st_join(oa.uk, retail, 
                     join = st_intersects) %>% #, 
                    #largest = TRUE) %>% # returns the x features augmented with 
                                         # the fields of y that have the largest 
                                         # overlap with each of the features of x
  as_tibble() %>% 
  filter(!is.na(RC_ID)) %>% 
  dplyr::select(id, RC_ID) %>% 
  add_row(id = "E00019779", RC_ID = "RC_EW_5951")

# If `larget = FALSE`, we have multiple RC_IDs for OAs.
# Also, RC_ID="RC_EW_5951" would fall in Thames as it is the London Bridge Tube Station.
# To avoid NAs for for n.nearest.retail, I would have assigned dist.retail.name = RC_EW_1935 for E00019779

# st_join(oa.uk, retail, join = st_is_within_distance, dist = 500) %>% 
#   as_tibble() %>% 
#   filter(!is.na(RC_ID)) %>% 
#   dplyr::select(id, RC_ID)
# 
# st_filter(oa.uk, retail,  .pred = st_is_within_distance, dist = 100) %>% 
#   as_tibble() %>% 
#   filter(!is.na(RC_ID)) %>% 
#   dplyr::select(id, RC_ID)

# h <- oa.uk %>% st_intersects(retail)

@@

retail.help <- df %>% full_join(retail.oa, by = c("oa11cd" = "id")) %>% 
  group_by(RC_ID, year) %>% 
  summarise(n.nearest.retail = sum(n)) %>% 
  mutate(n.nearest.retail.lag = dplyr::lag(n.nearest.retail)) %>% 
  ungroup()

@@

df <- df %>% left_join(retail.help, by = c("dist.retail.name" = "RC_ID", "year" = "year"))
#sapply(df, function(x) sum(is.na(x)))
```

### Urban Rural TODO

@@

```{r}
# Lookup: OA to regions
# **FIXED< DELETE IN TEST** NEED TO ADD NI. NOT A PROBLEM FOR NOW AS IT IS FIXED IN THE TEST SECTION

@@

```{r}
# sf_use_s2(FALSE)
# oa.c <- st_centroid(oa.uk)
# kn <- knearneigh(oa.c, k = 5)
# knn <- knn2nb(kn, row.names = NULL, sym = FALSE)
# knn.l <- nb2listw(knn)

path.out <- paste0(path, "/data/temp/knnl.RData")
# save(knn.l, file = path.out)
load(path.out)

@@

# Lookup: OA to regions
path.lookup <- paste0(path, "/data/raw/Output_Area_to_Region_(December_2011)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% dplyr::select(OA11CD, RGN11CD, RGN11NM)

# For growth:
df <- df %>% group_by(oa11cd) %>% 
  mutate(#n.lag = dplyr::lag(n),
         growth = log(n/n.lag),
                    abs.growth = n - n.lag) %>% 
  relocate(n.lag, .after = n)

# out.path <- paste0(path, "/data/temp/df_for_oa_rf.csv")
# df <- read_csv(out.path)
# df %>% write_csv(file = out.path)

# rm(list=setdiff(ls(), "df"))

# # This is the project path
# path <- find_rstudio_root_file()

@@

# There are no lags for 1996, so it is removed
df <- df %>% filter(year > 1996) %>% 
  dplyr::select(oa11cd, year, RGN11CD, n, abs.growth, n.l.slag, n.nearest.city.lag, 
                n.nearest.retail.lag, n.London.lag, London, dist, dist.retail) #%>% #growth, abs.growth, RGN11NM, 
  # mutate(London.v = n.London.lag / London,
  #        city.v = n.nearest.city.lag / dist,
  #        retail.v = n.nearest.retail.lag / (dist.retail + .1)) %>% 
  # dplyr::select(-n.London.lag, -London, -n.nearest.city.lag, -dist, -n.nearest.retail.lag, -dist.retail)

@@

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken #20.6h

@@

#folds
k <- 10 #

@@

@@

regions <- df %>% ungroup() %>% distinct(RGN11CD) 
regions <- as.vector(regions$RGN11CD)

@@

  print(paste0("start loop for ", i))

@@

  model.all <- train(n ~ n.London.lag + n.nearest.city.lag + n.nearest.retail.lag + n.l.slag + year + London + dist + dist.retail,
                   data = df %>% filter(RGN11CD!=i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  #assign(paste0("model.all",as.character(i)), model.all)

  file <- paste0(path, "/outputs/rf/models/oa_rf/regions/region_", as.character(i), ".RData")
  save(model.all, file = file)  # file name = region not in the training data
  rm(model.all)

  print(paste0("end loop for ", i))

}

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken
```

@@

```{r}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

for (i in filenames){
  load(file = i)
  i <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  assign(i, model.all)  
}

@@

```{r}
# train on all but one region, test on that region

df.predictions <- data.frame()
for (i in regions){
  #for (j in regions[!regions == i]){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("region_", i)], 
                    df[df$RGN11CD==i,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", ".on.", i), pred)

    d <- paste0("region.predict.model.", ".on.", i)
    d <- cbind(get(d), df %>% filter(RGN11CD==i)) #%>% arrange(year, ladcd)

    #***dplyr::select(RGN21CD, ladcd, year, growth, 1)***

    d <- d[,c(5, 2, 4, 6, 1)]     
    colnames(d)[5] <- "predictions"
    d <- d %>% mutate(trained.on = i)
    df.predictions <- rbind(d, df.predictions)
  #}
}

### OLD

```{r, eval=FALSE}
# train on all but one region, test on that region
